---
title: "Interaction"
author: "Ian_Curtis"
date: "2018/11/27"
output:
  html_document: default
  word_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
# install & load packages
# install.packages("readxl")
library(readxl)
library(tidyverse)
library(ggplot2)
library(corrplot)
```

## Interaction Overview

<!-- Comment About Interaction -->

## Interaction R Part A

### import data

```{r importdata}
IceCreamExcel <- read_excel('IceCreamExcel.xlsx')
head(IceCreamExcel)
str(IceCreamExcel)
summary(IceCreamExcel)
```

### exclude variable x(id) 

```{r ICD}
ICD <- subset(IceCreamExcel, select = -c(id))
str(ICD)
summary(ICD)
```

### run correlations

```{r correlations}
cor(ICD)
```
The correlation matrix show us that,the correlation in variable *temp* and *cons*  is about **0.788**,which mean these two variable have strong correlationship.And  the other variables are almost independent.

### corr visualization

```{r}
corr <- cor(ICD)
# corrplot::corrplot(corr = corr)
corrplot::corrplot(corr = corr, order = "AOE", tl.pos = "tp")
corrplot::corrplot(corr = corr,  
         add = TRUE, type = "lower", method = "number", order = "AOE", 
         col = "black", diag = FALSE, tl.pos = "n", cl.pos = "n")
```
The correlations plot only is an another method for explanation of correlation matrix,what it tells us is the same.

### use Hmisc
```{r usehmisc}
library(Hmisc)
rcorr(as.matrix(ICD))
```
The **rcoor** is not only provided correlation matrix,it also provide test in correlation across variable.And only *p-value* in test of *temp* and *cons* is smaller than 0.05,that is ,*temp* is correlated with *cons*


## Interaction R Part B

### create some new var, run correlations 

```{r}
ICD <- ICD %>% mutate(
    Income_by_price = income * price,
    Income_by_temp  = income * temp ,
    Price_by_temp   = price * temp
) %>% mutate(
    income_mc = scale(income, center = TRUE),
    price_mc  = scale(price, center = TRUE),
    temp_mc   = scale(temp, center = TRUE)
)

summary(ICD)
rcorr(as.matrix(ICD))
```

### create two_way interaction terms and view corr

```{r}
ICD <- ICD %>% mutate(
    Income_by_price = income_mc * price_mc,
    Income_by_temp  = income_mc * temp_mc ,
    Price_by_temp   = price_mc * temp_mc
)

summary(ICD)
rcorr(as.matrix(ICD))
```
This step add variable interaction term in raw data.

## Interaction R Part C
### testing linear model w/no interactions
```{r}
model <- lm(cons ~ income + price + temp, data = ICD)
summary(model)
library(car)

vif(model)
```
According to the result of this model,and the function **Vif** ,which compute each variable's **Variance Inflation Factors**;and vif value in each variable is smaller than 10,which mean that  collinearity  in model does not exist.And the *R.Square* in thsis model is about **0.68**.

### testing linear model w/no interactions without pequod, note use of mean center predictoros

```{r}
model1 <- lm(cons ~ income + price + temp + Income_by_temp + 
                 Income_by_price + Price_by_temp, data = ICD)
summary(model1)
vif(model1)
```
This new model add interaction term.Accordding to the summary of the new model,we can know that all predictors'**Variance Inflation Factors**  in this model ara still smaller than 10,which mean that  collinearity  in new model does not exist too,but in **R.Square** is about **0.72**,that is to said this model perform better than origin model.

### testing linear model w/no interactions using pequod

```{r}
library(pequod)

modelpe <- lmres(cons ~ income + price + temp, data = ICD)
summary(modelpe)

modelpe1 <- lmres(cons ~ income * price + income * temp + price * temp, 
                 centered = c("income", "price", "temp"), data = ICD)
summary(modelpe1)
```

In model that lack of interactions,the coefficient of *income* and *temp* is significant,and these two variables both has positive effect on response *cons*;But in the model that add interactions,the coefficient of *itercept*,*temp* and *iteraction of income and price* are significant.The  coefficient result change,but the latter model perform better based on *R.Square*.However,the coefficient of interaction is greater than other,and is is negative,that is ,the interaction has a more greater effect on response.And the comparion between the two model,interaction term should add in linear model.

## Interaction R Part D

### Simple slope test and plot for income by price interatcion

```{r}
S_slopes <- simpleSlope(modelpe1, pred = "income", mod1 = "price")
PLotIncome_by_proce <- PlotSlope(S_slopes)
PLotIncome_by_proce
summary(S_slopes)
```

The result show us that,the slope is significant when price is low,and is not sigificant when price is high.And the *cons* change whether is positive or not is  effect signifivantly by price

## Interaction R Part E
### creating and testing:
testing three-way interactions without pequod, note use of maen center predictors

```{r}
ICD <- ICD %>% mutate(threeway = income_mc * price_mc * temp_mc)
model2 <- lm(cons ~ income + price + temp + Income_by_temp + 
                 Income_by_price + Price_by_temp + threeway, data = ICD)
summary(model2)
vif(model2)

modelpe2 <-  lmres(cons ~ income * price * temp, 
                 centered = c("income", "price", "temp"), data = ICD)
summary(modelpe2)
```
According to  the models show us that,the result is  the model with threeway interaction perform better based on *R.Square*,The *R.Square* is about 0.75.And other resultr is simliar with the model with twoway interaction.However,in this time,the coefficinet of interaction of income_price,income_temp,income_price_temp are sigificant,and the effect of them are all negative on response.

### Simple slope test and plot for the three-way interatcion
```{r}
S_slopes_3way <- simpleSlope(modelpe2, pred = "income", mod1 = "temp", mod2 = "price")
Plot_threeway <- PlotSlope(S_slopes_3way)
Plot_threeway
summary(S_slopes_3way)
```

According to the result of this test,the slope  change sinifcant when temp,price change,which indicates that the *cons* is mianly effect by *income* and *temp*
 
In conclusion,*price* and *temp* are the main effective factor on response *cons*,and their interaction ,treeway interaction  still  have effect on *cons*,but inetractions' effect is less.



