---
title: "Econ 4010 Homework 6"
author: "RyanYip"
output:
  word_document: default
  html_document: default
---

```{r,warning=FALSE,echo=FALSE}
library(quantmod)
library(stringr)
library(tseries)
library(ggplot2)
Sys.setlocale("LC_TIME", "American")
```


```{r,echo=FALSE}
FITB=as.data.frame(getSymbols("FITB",auto.assign = FALSE,src = "yahoo",from="2018-01-01",to="2018-10-01"))

KR=as.data.frame(getSymbols("KR",auto.assign = FALSE,src = "yahoo",from="2018-01-01",to="2018-10-01"))

dim(FITB)[1]
dim(KR)[1]
```


## Question 1
```{r,echo=FALSE}
time=as.Date(rownames(FITB))
Investment=as.numeric(FITB[,4])
FITB.returns=Investment/Investment[1]  # returns

plot(time,FITB.returns,type="l",col="red",xlab = "")
```

## Question 2
```{r,echo=FALSE}
Investment_diff= diff(FITB.returns,lag=1,trim=TRUE)
Investment_diff = Investment_diff[!is.na(Investment_diff)]

# Plot log returns 
plot(time[-1],Investment_diff,type='l', main=NULL,xlab ="",ylab = "Investment difference",col="red")
```


## Question 3
```{r,echo=FALSE}
apply(FITB,2,sd)

acf(ts(FITB.returns))
pp.test(ts(FITB.returns),alternative = "stationary")
```

According to the ACF plot,The above ACF is ¡°decaying¡±, or decreasing, very slowly, and remains well above the significance range (dotted blue lines). This is indicative of a non-stationary series.And the ** Phillips¨CPerron Unit Root Test ** also tells us that ,the p-value of test is greater 0.05,which indicates that it is not significant.So,we can conclude that,this variable is not stationary.


## Question 4
```{r,echo=FALSE}
KR.Investment=KR[,4]
KR.returns=KR.Investment/KR.Investment[1]  # returns to Kroger stock

acf(ts(KR.returns))
pp.test(ts(KR.returns),alternative = "stationary")
```
According to the result got from above analysis,the analysis process and result is same as Question 3.So this variable is not stationary.


#### Plot the difference of KR returns
```{r,echo=FALSE}
KR.returns.diff=diff(KR.Investment)
plot.ts(ts(KR.returns.diff))


sprintf("pp test on difference of KR returns \n")
pp.test(ts(KR.returns.diff))
```
The plot and pp test  shows that the difference of KR returns is stationary.


## Question 5
```{r,echo=FALSE}

KR.returns.lag_1=lag(KR.returns.diff,-1)
KR.returns.lag_2=lag(KR.returns.diff,-2)

FITB.returns.diff=diff(FITB.returns)
FITB.returns.lag_1=lag(FITB.returns.diff,-1)
FITB.returns.lag_2=lag(FITB.returns.diff,-2)

Data=data.frame(KR.diff=as.numeric(KR.returns.diff),
                KR.lag_1=as.numeric(KR.returns.lag_1),
                KR.lag_2=as.numeric(KR.returns.lag_2),
                FITB.lag_1=as.numeric(FITB.returns.lag_1),
                FITB.lag_2=as.numeric(FITB.returns.lag_2))

```

```{r,echo=FALSE,warning=FALSE}
model=lm(KR.diff~KR.lag_1+KR.lag_2+FITB.lag_1+FITB.lag_2,data=Data)
summary(model)
```

According to the summary of regression model,the coefficient of lag 1 on difference of returns to FITB if significant,which indicates that lag 1 on FITB affect the difference of returns to Kroger stock.

## Question 6
```{r,echo=FALSE}
HWTrends<-read.csv("./HWTrends.csv",header = TRUE)
Ham=HWTrends$Ham

par(mfrow=c(1,3))
pacf(Ham)
acf(Ham)
plot.ts(ts(Ham))
adf.test(Ham,alternative = "stationary")
```

The graph show us that,the acf ,pacf decay quikly,and ts plot has not obvious trend.
we also call the ADF test on the Ham series data to check for stationarity. The p-value of  0.01   from the ADF test tells us that the series  Ham  is stationary



## Question 7
```{r,echo=FALSE}
Caddyshack=HWTrends$Caddyshack

par(mfrow=c(1,3))
pacf(Caddyshack)
acf(Caddyshack)
plot.ts(ts(Caddyshack))
adf.test(Caddyshack,alternative = "stationary")
```
The result is same as the question 6(Ham variable).And we get the same conclusion.So variable Caddyshack is stationary

## Question 8
```{r,echo=FALSE,eval=FALSE}
Caddyshack=ts(HWTrends$Caddyshack)
Caddyshack_lag5=lag(Caddyshack,lag = -5)

plot(Caddyshack_lag5,main="Lag 5 on Caddyshack")
```

### Fit Autoregressive Models on Caddyshack 
```{r,echo=FALSE}
model=ar(Caddyshack,aic = TRUE,order.max = 5)
model
```
According to the result above,the model best lag is `r model$order `


## Question 9
```{r,echo=FALSE}
Ham_lag3=lag(Ham,-3)
LeftOvers=HWTrends$Leftovers
LeftOvers_lag2=lag(LeftOvers,-2)

ccf(Ham,LeftOvers,main="Ham vs LeftOvers",ylab = "cross-correlation")
```
According to the  CCF graph  acrross variable Ham and LeftOvers ,It has strong correlation for lags -3 to 0 with tapering in both directions.



#### Run linear regression

Formula:  c(Leftovers_lag_1,Leftovers_lag_2) ~ Ham_lag_1+Ham_lag_2+Ham_lag_3

```{r}
Data=data.frame(LeftOvers_lag_1=lag(LeftOvers,-1),
                LeftOvers_lag_2=lag(LeftOvers,-2),
                Ham_lag_1=lag(Ham,-1),
                Ham_lag_2=lag(Ham,-2),
                Ham_lag_3=lag(Ham,-3))
```

```{r,echo=FALSE}
lm.model=lm(cbind(LeftOvers_lag_1,LeftOvers_lag_2)~0+Ham_lag_1+Ham_lag_2+Ham_lag_3,data=Data)
summary(lm.model)
```
According to summary of the regression model, the coefficients of the Ham lag 1 is significant,which indicates that the lag 1 of Ham  has strong correlation accross LeftOvers_lag_1 and LeftOvers_lag_2. So I have reason to believe searches for ¡°Ham¡± affect the number of searches for ¡°Leftovers¡±.


## Question 10

*  H0:  remove variable Ham from regression  model with responce Leftovers
*  H1:  not remove variable Ham from regression  model with responce Leftovers

```{r,echo=FALSE,warning=FALSE}
library(lmtest)
df=HWTrends[,c("Ham","Leftovers")]
```


#### stationary test
```{r}
adf.test(df$Ham)
```

According to the adf.test,Ham is stationary

#### Granger causality test 
```{r,echo=FALSE}
lmtest::grangertest(Leftovers~Ham,data=df,order=3)
```
The p-value of the above result is 0.1734,which tells us that we can not reject the H0.According to the test,we can not conclude that whether this variable can use to be a predictor  for Leftovers.
